%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Class
% Version 2.0 (12/10/23)
%
% This class originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Omar Roldan
% Based on a template by  Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended
\usepackage{multicol}
\setlength{\columnsep}{0mm}
%----------------------------------------------------------------------------------------
\usepackage{lipsum}  


\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.5\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	{ \fontsize{16}{20} \textcolor{black}{\textbf{\MakeUppercase{Alaa Abdelbaki}}}} % First name

	\vspace{6pt}

	{\Large Mobile developer} % Career or current job title
\end{minipage}
\hfill
\begin{minipage}[t]{0.2\textwidth} % 20% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% \icon{Globe}{11}{\href{http://alaaabdelbaki.github.io}{alaaabdelbaki.github.io}}\\
	\icon{Phone}{11}{+216 41 675 757}\\
	\icon{MapMarker}{11}{Ariana, Tunisia}\\

\end{minipage}
\begin{minipage}[t]{0.27\textwidth} % 27% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\icon{Envelope}{11}{\href{mailto:alaa.abdelbaki@outlook.com}{alaa.abdelbaki@outlook.com}}\\
	\icon{Github}{11}{\href{https://github.com/AlaaAbdelbaki}{github.com/AlaaAbdelbaki}}\\
	\icon{LinkedinSquare}{11}{\href{https://www.linkedin.com/in/AlaaAbdelbaki}{/in/AlaaAbdelbaki}}\\

\end{minipage}


%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.46\textwidth}
	\cvsect{Summary}
	\vspace{-6pt}

	I'm a mobile software engineer, with 2 years of experience in developing cross platform applications with the Flutter framework.\\
	While developing mobile applications, I had the chance to also work on their backend, and ensure submitting them on the Google Play Store and the Apple App Store.
\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.465\textwidth}
	\cvsect{Skills}
	\vspace{-6pt}

	\begin{minipage}[t]{0.2\textwidth}
		\textbf{Languages:}
	\end{minipage}
	\hfill
	\begin{minipage}[t]{0.73\textwidth}
		Dart, Java, Kotlin, Swift, Javascript, C\#.
	\end{minipage}
	\vspace{4mm}

	\begin{minipage}[t]{0.2\textwidth}
		\textbf{Technologies:}
	\end{minipage}
	\hfill
	\begin{minipage}[t]{0.73\textwidth}
		Flutter, Git, Android, iOS, Jenkins, NestJS, ExrpessJS, NextJS.
	\end{minipage}

\end{minipage}



%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------
\newcommand{\printlist}[1]{%
	\foreach \x [count=\xi] in {#1} {\texttt{\x} \slashsep }%
}
\vspace{10 pt}
\cvsect{Experience}
\begin{entrylist}
	\entry
	{07/2023 -- Present}
	{Flutter developer}
	{\href{https://www.e-butler.com}{EButler}}
	{\vspace{-10pt}
		\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
			\item Added new features to an existing Flutter application.
			\item Worked on improving the real-time chatting feature using GetStream's Stream Chat library.
			\item Maintained legacy code.
			\item Upgraded the project to newer SDK versions, while performing the required code changes.
			\item Pushed updates through the Google Play Store.
			\item Developed a redesigned version for mobile and web platforms while referencing a Figma design.
			\item Implemented new features and perform updates on a NestJS backend.
		\end{itemize}
		\printlist{Flutter,NestJs,Firebase,Firebase Cloud Messaging,GetStream,Google Play,App Store,WhatsApp Business API}}
	\entry
	{01/2022 -- 06/2023}
	{Software Engineer}
	{\href{https://www.swisspremiumnegoce.com}{Swiss Premium Negoce}}
	{\vspace{-10pt}
		\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
			\item Defined the project's usecases and requirements.
			\item Decided which technologies to use based on the technical requirements.
			\item Created the database design.
			\item Developed the mobile application's UI based on an Adobe XD design.
			\item Added new features and updating existing ones.
			\item Developed backend features.
			\item Write backend documentatio
			\item Implemented Google Cloud APIs in the mobile application (Google Maps / Google Directions)
			\item Integrated Stripe as a payment Gateway.
			\item Submitted and releacing the application on the Google Play Store and the Apple App Store.
		\end{itemize}

		\printlist{Flutter,Firebase,Firebase Cloud Messaging, Google Maps API, Google Directions API, ExpressJS, Stripe}}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\vspace{-10 pt}
\cvsect{Education}
\begin{entrylist}
	\entry
	{09/2018 - 06/2022}
	{Engineering degree in computer science}
	{\href{https://www.esprit.tn}{Private Higher School of Engineering and Technology (ESPRIT)}}
	{Followed the computer science program, and specialized in mobile applications development\\Worked on multiple projects in different fields during the cursus, including:
		\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=0pt]
			\item Mobile development.
			\item Web development.
			\item Artificial intelligence.
			\item computer vision.
			\item DevOps.
		\end{itemize}
	}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	Projects
%----------------------------------------------------------------------------------------
\cvsect{Projects}
\begin{entrylist}
	\entry
	{Flutter / ExpressJS}
	{Elisys}
	{
		% GithubLink
	}
	{
		A warehouse management mobile application, that helps technicians manage their products by simply scanning a QR code.
	}
	\entry
	{Flutter}
	{Doroos}
	{
		% GithubLink
	}
	{
		An online learning application, where users can choose from a wide variety of subjects and teachers, and chat with them in real time.
	}
\end{entrylist}




%----------------------------------------------------------------------------------------
%	LANGUAGES
%----------------------------------------------------------------------------------------
\vspace{-10 pt}
\cvsect{Languages}
\vspace{-6pt}

\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=0.18\textwidth]
	\item \textbf{English} - Fluent
	\item \textbf{French} - B2
	\item \textbf{Arabic} - Native
\end{itemize}

% \hspace{26mm} \textbf{English} - Fluent, \textbf{ French} - B2, \textbf{ Arabic} - Native

%----------------------------------------------------------------------------------------

\end{document}